Cleaning, Disinfection, and Mapping Robot

### 2020-12-23 cleaningRobotDescription.tex

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{amssymb}
\author{Brian Lauer}

\begin{document}

\begin{figure}
\centering
\includegraphics[scale=0.5]{figs/img/frontViewScreenshotB}
\caption{Current cleaning, disinfection, and mapping robot design}
\label{camRobot}
\end{figure}

Many different robots exist on the market for the purpose of UV disinfection from companies like UVD Robots. These robots typically employ sensors like ultrasonic sensors for ranging, LIDAR sensors or cameras for generation of a digital map of a room, and cliff sensors for recognition of drops or edges. One of the main features they employ is a UVC lamp that is capable of performing efficient elimination of many harmful microorganisms including bacteria and viruses within a room through DNA destruction and disruption. However, a limitation to these current robots on the market is the inability to shine UV light vertically: only horizontally with full 360$^\circ$ range of emission. The proposed robot design shown in Figure \ref{camRobot} will support emission of light horizontally as well as vertically by including two horizontally positioned lamps able to disinfect areas directly above the robot. Secondly, because UV light is deemed dangerous to humans and possibly other animals a disinfection sprayer will help to further reduce the concentration of harmful pathogens. In this way, full room disinfection can be accounted for in case any live animals are unable to be relocated during the disinfection period. During disinfection of a room with UVC light such as a hospital room, no humans or animals may be present. To provide a maximum turning radius and stability, the robot features a two-wheel differential drive design with two additional points of contact via two caster wheels. For creation of a digital map, a LIDAR sensor is present in the center of the robot which will relay serial data to the robot's central computer, a Beaglebone single board computer with the SLAM (Simultaneous Localization and Mapping) algorithm.

@@

>>>>

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fullpage}
\title{Cleaning, Disinfection, and Mapping Robot}
\author{Brian Lauer\and Suruz Miah}

\begin{document}
\maketitle

Nowadays, many different robots are available on the market for the purpose of
ultraviolet (UV) disinfection from companies like UVD
Robots\footnote{http://www.uvd-robots.com/}. These robots typically employ
sensors, such as ultrasonic sensors for ranging, LIDAR sensors or cameras for
creating a map of a room, and cliff sensors for recognition of
drops or edges. One of the main features of these robots is to utilize UVC lamp that is
capable of performing efficient elimination of many harmful microorganisms
including bacteria and viruses within a room through DNA destruction and
disruption. However, a limitation to these current robots on the market is the
inability to shine UV light vertically: only horizontally with full 360$^\circ$
range of emission. The proposed robot design shown in Figure~\ref{camRobot} will
support emission of light horizontally as well as vertically by including two
horizontally positioned lamps able to disinfect areas directly above the
robot. %
%
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.5]{figs/img/frontViewScreenshotB}
  \caption{Current cleaning, disinfection, and mapping robot design}
  \label{camRobot}
\end{figure}
%
Secondly, because UV light is deemed dangerous to humans and possibly other
animals a disinfection sprayer will help to further reduce the concentration of
harmful pathogens. In this way, full room disinfection can be accounted for in
case any live animals are unable to be relocated during the disinfection period.
During disinfection of a room with UVC light such as a hospital room, no humans
or animals may be present. To provide a maximum turning radius and stability,
the robot features a two-wheel differential drive design with two additional
points of contact via two caster wheels. To generate a digital map, a LIDAR
sensor is present in the center of the robot which will relay serial data to the
robot's central computer, a Beaglebone single board computer with the SLAM
(Simultaneous Localization and Mapping) algorithm.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
